---
title: "Model"
subtitle: "What is the most correlated variable to listen to to increase happiness levels?"
author: "Thomas Seoh"
format: html
execute:
  echo: FALSE
  message: FALSE
  warning: FALSE
---

```{r}
#| label: setup
#| message: false
#| warning: false
library(tidyverse)
library(primer.data)
library(brms)
library(tidybayes)
library(gtsummary)

df <- read_csv("data/world-happiness-report-updated_2024.csv")
```

To answer the question of which factor correlates most with happiness, we have to see which of the variables are most associated with levels of happiness, by using a Bayesian Linear Regression Model. For this model, we are using this formula:

$$
\text{happiness} = \beta_{0} + \beta_{1} \cdot \text{social_support} + \beta_{2} \cdot \text{income} + \beta_{3} \cdot \text{health} + \beta_{4} \cdot \text{freedom} + \beta_{5} \cdot \text{generosity} + \beta_{6} \cdot \text{perceptions\_of\_corruption}
$$

```{r}
# Filter and rename columns as needed
happiness_data_filtered <- df |> 
  rename(
    social_support = "Social support",
    income = "Log GDP per capita",
    health = "Healthy life expectancy at birth",
    freedom = "Freedom to make life choices",
    generosity = "Generosity",
    perceptions_of_corruption = "Perceptions of corruption",
    happiness = "Life Ladder"
  ) |> 
  select(happiness, social_support, income, health, freedom, generosity, perceptions_of_corruption) |> 
  filter(
    !is.na(social_support), 
    !is.na(income), 
    !is.na(health), 
    !is.na(freedom), 
    !is.na(generosity), 
    !is.na(perceptions_of_corruption), 
    !is.na(happiness)
  )
```

We see that on average, higher levels of social support generally have higher levels of happiness. Note that the Perceptions of Corruptions should be reversed, as it is a scale from lowest to highest (best to worst).

```{r}
#| label: general analysis
#| cache: true

fit <- brm(
  formula = happiness ~ social_support + income + health + freedom + generosity + perceptions_of_corruption,
  data = happiness_data_filtered,
  family = gaussian(),
  refresh = 0,
  silent = 2,
  seed = 123
)

tbl_regression(fit)
```

```{r}
df1 <- read_csv("data/world-happiness-report-updated_2024.csv") |>
  rename(
    social_support = "Social support",
    income = "Log GDP per capita",
    health = "Healthy life expectancy at birth",
    freedom = "Freedom to make life choices",
    generosity = "Generosity",
    perceptions_of_corruption = "Perceptions of corruption",
    happiness = "Life Ladder"
  ) |>
  select(happiness, social_support, income, health, freedom, generosity, perceptions_of_corruption) |>
  filter(
    !is.na(social_support), 
    !is.na(income), 
    !is.na(health), 
    !is.na(freedom), 
    !is.na(generosity), 
    !is.na(perceptions_of_corruption), 
    !is.na(happiness)
  )
```

```{r}
#| label: detailed analysis
#| cache: true

fit_all <- brm(
  formula = happiness ~ social_support + income + health + freedom + generosity + perceptions_of_corruption,
  data = df1,
  family = gaussian(),
  refresh = 0,
  silent = 2,
  seed = 123
)

fit_all
```

